Informing policy via dynamic models: Cholera in Haiti

### 2024-01-23 ms.Rnw
Incorporated changes to Model3 fitting process

<<CalculateLee1Likelihoods, echo=FALSE, message=FALSE, include=FALSE>>=

@@

<<LoadModel1Params, echo=FALSE, message=FALSE, include=FALSE>>=

# This code chunk is used to fit Model 1 using the IF2 algorithm.
set.seed(636813)

@@

<<FitModel2, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE>>=

@@

# TODO: Model 2

@@

    model2_fit_results <- list()
    model2_fit_results[['h2_params']] <- h2_params
    model2_fit_results[["n_fit_params"]] <- n_fit_params
    model2_fit_results[['logLik']] <- h2_fit_tmp$value

@@

<<FitModel3, echo=FALSE, include=FALSE, message=FALSE>>=

# This code chunk is used to fit Model 3 using the IBPF algorithm.
set.seed(8636712)

# Create vectors for the unit and shared parameters
unit_specific_names <- c("betaB", "foi_add", "aHur", "hHur", "Iinit")
shared_param_names <- c(
  "mu_B", "XthetaA", "thetaI", "lambdaR", "r", "std_W",
  "epsilon", "k"
)
est_param_names <- c(
  unit_specific_names, shared_param_names
)

# Add unit numbers to each parameter
est_param_names_expanded <- paste0(rep(est_param_names, each = 10), 1:10)

# Simple function that is used to set the rw_sd for the first search
# This function is convenient so that we don't have to type out the rw_sd
# for each unit parameter.
set_rw_1 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.01)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.015, 0)))
  } else if (x %in% c("Iinit3", "Iinit4")) {
    return(expression(ivp(0.25)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.015)
  } else if (grepl('^betaB[[:digit:]]+$', x)) {
    return(0.01)
  } else {
    return(0)
  }
}

set_rw_2 <- function(x) {
  if (gsub("[[:digit:]]+$", "", x) %in% shared_param_names) {
    return(0.003)
  } else if (x %in% paste0(rep(c("aHur", 'hHur'), each = 2), c(3, 9))) {
    return(expression(ifelse(time >= 2016.754 & time <= 2017, 0.005, 0)))
  } else if (x %in% c("Iinit3", "Iinit4")) {
    return(expression(ivp(0.125)))
  } else if (grepl('^foi_add[[:digit:]]+$', x)) {
    return(0.005)
  } else if (grepl('^betaB[[:digit:]]+$', x)) {
    return(0.003)
  } else {
    return(0)
  }
}

# First Search RW
reg_rw_1.sd <- lapply(est_param_names_expanded, set_rw_1)
names(reg_rw_1.sd) <- est_param_names_expanded
chol_rw_1.sd <- do.call(rw_sd, reg_rw_1.sd)

# Second Search RW
reg_rw_2.sd <- lapply(est_param_names_expanded, set_rw_2)
names(reg_rw_2.sd) <- est_param_names_expanded
chol_rw_2.sd <- do.call(rw_sd, reg_rw_2.sd)

if (RUN_LEVEL == 1){
  SEARCH1 = list(
    NBPF = 10,
    NP = 200,
    SPAT_REGRESSION = 0.05,
    NREPS = 20,
    NP_EVAL = 200,
    NREPS_EVAL = 3,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

  SEARCH2 = list(
    TOP_N = 8,
    NBPF = 10,
    NP = 200,
    SPAT_REGRESSION = 0.05,
    NREPS = 2,
    NP_EVAL = 200,
    NREPS_EVAL = 3,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

} else if (RUN_LEVEL == 2) {
  SEARCH1 = list(
    NBPF = 100,
    NP = 1000,
    SPAT_REGRESSION = 0.05,
    NREPS = 72,
    NP_EVAL = 1000,
    NREPS_EVAL = 8,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )

  SEARCH2 = list(
    TOP_N = 9,
    NBPF = 100,
    NP = 1000,
    SPAT_REGRESSION = 0.05,
    NREPS = 4,
    NP_EVAL = 1000,
    NREPS_EVAL = 9,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )

} else if (RUN_LEVEL == 3) {

  SEARCH1 = list(
    NBPF = 100,
    NP = 2500,
    SPAT_REGRESSION = 0.05,
    NREPS = 144,
    NP_EVAL = 2500,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = FALSE,
    KEEP_LIKE_MAT = FALSE
  )

  SEARCH2 = list(
    TOP_N = 12,
    NBPF = 100,
    NP = 2500,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 2500,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = FALSE,
    KEEP_LIK_MAT = TRUE
  )
}

# Calculate the number of parameters that are estimated:
# This is calculated by the number of non-zero rw_sd values (including expressions), but then subtracting of repeated shared parameters.
mod3_n_params <- sum(reg_rw_1.sd != 0, na.rm = TRUE) + sum(sapply(reg_rw_1.sd, is.expression)) - length(shared_param_names) * 9

# Fit Model 3
haiti3_fit <- readRDS("model3/run_level_3/haiti3_fit.rds")
# haiti3_fit <- bake(
#   file = paste0("model3/", rl_dir, "haiti3_fit.rds"), {
#     fit_haiti3(
#       nsearches = 2L,
#       search1 = SEARCH1,
#       search2 = SEARCH2,
#       search_rho = FALSE,
#       search_gamma = FALSE,
#       search_Iinit = TRUE,
#       search_hur = TRUE
#     )
#   }
# )

# haiti3_fit contains ll estimate for many parameter sets, so we want to find
# the highest value
mod3_ll <- max(
  haiti3_fit[[length(haiti3_fit)]]$logLiks$logLik,
  na.rm = TRUE
)

# Just a bit of tidying up: removing parameters that we won't use again.
rm(
  SEARCH1, SEARCH2, N_SEARCHES,
  est_param_names, est_param_names_expanded,
  set_rw_1, set_rw_2, set_rw_3, reg_rw_1.sd, reg_rw_2.sd, reg_rw_3.sd,
  chol_rw_1.sd, chol_rw_2.sd, chol_rw_3.sd
)
gc()

<<createModelObjects,echo=FALSE,eval=TRUE, include=FALSE, message=FALSE>>=

# Find the index for parameters of model 3 that correspond to the MLE.
best_m3 <- which.max(haiti3_fit[[length(haiti3_fit)]]$logLiks$logLik)

# Save the parameters that correspond to the MLE of Model 3.
p3 <- haiti3_fit[[length(haiti3_fit)]]$params[best_m3, ]

@@

<<AICtableInput, echo=FALSE, eval=TRUE>>=
NREPS_EVAL <- switch(RUN_LEVEL,   3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL, 100, 500,  5000)

@@

# Calculate likelihood via block-particle filter
mod3_eval_res <- readRDS("model3/run_level_3/mod3_eval_res.rds")
# mod3_eval_res <- bake(
#   file = paste0('model3/', rl_dir, 'mod3_eval_res.rds'), {
#
#     # Create a list to store results
#     results <- list()
#
#     coef(h3Spat) <- p3
#
#     # Perform block-particle filter
#     h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
#       bpfilter(h3Spat, Np = NP_EVAL, block_size = 1)
#     }
#
#     ll <- logLik(h3_bpf)
#     results$ll <- logmeanexp(ll[!is.na(ll)], se = FALSE)
#
#     ### Get likelihood for subset of the data
#
#     # Find appropriate sub-set
#     in_subset_cols <- h3_bpf[[1]]@times >= as.numeric(lubridate::decimal_date(as.Date("2014-03-01")))
#     in_subset_rows <- h3_bpf[[1]]@unit_names != 'Ouest'
#
#     mod3_coupled_subset_evals <- c()
#     for (i in 1:length(h3_bpf)) {
#       mod3_coupled_subset_evals <- c(
#         mod3_coupled_subset_evals,
#         sum(h3_bpf[[i]]@block.cond.loglik[in_subset_rows, in_subset_cols])
#       )
#     }
#
#     results$subset_ll <- logmeanexp(mod3_coupled_subset_evals)
#     results
#   },
#   timing = FALSE
# )

@@

<<CalculateBenchLikelihood, echo=FALSE, message=FALSE, include=FALSE, cache=TRUE>>=

@@

benchmarks[['m3']] <- m3_benchmark
rm(cases, m3_benchmark, m3_bench, dep, mod3_cases)
gc()
@

<<AIC Lee et al, echo=FALSE, include=FALSE, message=FALSE>>=
lee3_NP   <- switch(RUN_LEVEL, 50, 250, 5000)
lee3_NREP <- switch(RUN_LEVEL,  3,   8,   36)

@@

# Create Lee et al (2020a) version of model 3 on sub-data
lee3_sub <- lee3_spatPomp()

lee3_all <- lee3_spatPomp(start_date = "2010-10-23")

lee3_results <- readRDS("model3/run_level_3/lee3_results.rds")
# lee3_results <- bake(
#   file = paste0('model3/', rl_dir, 'lee3_results.rds'), {
#
#     # Create lists to save results
#     lee3_results <- list()
#
#     # Save how long it takes for sub-data
#     lee3_results[["sub_bpf_time"]] <- system.time({
#
#       lee3_sub_ll_evals <- foreach(
#         i = 1:lee3_NREP, .combine = rbind
#       ) %dopar% {
#
#         liks <- numeric(10L)
#
#         lee_bpf_out <- bpfilter(lee3_sub, block_size = 1, Np = lee3_NP)
#         Ouest_ind <- which(lee_bpf_out@unit_names == "Ouest")
#
#         for (u in 1:10) {
#           if (u == Ouest_ind) {
#             liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, lee3_sub@times >= lubridate::decimal_date(as.Date('2017-06-10'))])
#           } else {
#             liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, ])
#           }
#         }
#
#         liks
#       }
#     })
#
#     # Save all likelihood evaluations
#     lee3_results[["sub_ll_eval"]] <- logmeanexp(rowSums(lee3_sub_ll_evals)[!is.na(rowSums(lee3_sub_ll_evals))])
#
#     registerDoRNG(2789131)
#
#     # Save how long it takes for all data
#     lee3_results[["all_pf_time"]] <- system.time({
#       # Save all likelihood evaluations
#
#       lee3_all_ll_evals <- foreach(
#         i = 1:lee3_NREP, .combine = c
#       ) %dopar% {
#         logLik(bpfilter(lee3_all, block_size = 1, Np = lee3_NP))  # Get likelihood evaluations
#       }
#
#       lee3_results[["all_ll_eval"]] <- logmeanexp(lee3_all_ll_evals[!is.na(lee3_all_ll_evals)])
#
#     })
#
#     lee3_results[["n_params"]] <- 29
#
#     lee3_results
#   },
#   timing = FALSE
# )

@@

mod3_lee_coupled_aic <- 2 * lee3_results$n_params - 2 * lee3_results$all_ll_eval

mod3_lee_coupled_partial_aic <- 2 * lee3_results$n_params - 2 * lee3_results$sub_ll_eval
@

@@

<<cleanUpBetatFig, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE>>=
suppressWarnings(
  rm(h1_prof_res, mcap_results)
)
gc()
@

@@

# Get quantiles of simulations from the calibrated Model 3.
h3_quants <- readRDS("model3/run_level_3/h3Sims.rds")
# h3_quants <- bake(
#   file = paste0('model3/', rl_dir, 'h3Sims.rds'), {
#
#     coef(h3Spat) <- p3
#     # Simulate from the fitted version of Model 3
#     h3_sims <- simulate(
#       h3Spat, nsim = h3_nsim, format = 'data.frame'
#     )
#
#     # For each department and time-point, calculate percentiles of the
#     # simulations
#     h3_sims %>%
#       rename(dep = unitname) %>%
#       group_by(dep, time) %>%
#       summarise(
#         q05 = quantile(cases, 0.025, na.rm = T),
#         mean = mean(cases, na.rm = T),
#         q50 = quantile(cases, 0.5, na.rm = T),
#         q95 = quantile(cases, 0.975, na.rm = T)
#       ) %>%
#       ungroup() %>%
#       mutate(
#         date = lubridate::date_decimal(time)
#       ) %>%
#       mutate(date = as.Date(lubridate::round_date(date, unit = 'day')))
#   },
#   timing = FALSE
# )

@@

<<Load Model 3 Vacc Scenarios, message=FALSE, include=FALSE>>=
NP_BPF <- switch(RUN_LEVEL, 50, 200, 2000)
NSIM   <- switch(RUN_LEVEL, 10,  50, 1000)

h3_bpf_end_stats <- readRDS("model3/run_level_3/h3_bpf_end_states.rds")
# h3_bpf_end_states <- bake(
#   file = paste0("model3/", rl_dir, "h3_bpf_end_states.rds"),
#   expr = {
#     coef(h3Spat) <- p3
#     h3_bpf <- bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
#     ss <- h3_bpf@saved.states
#     ss[[length(ss)]]
#   },
#   timing = FALSE
# )

mod3_V0_res <- readRDS("model3/run_level_3/mod3_V0_res.rds")
# mod3_V0_res <- bake(
#   file = paste0("model3/", rl_dir, "mod3_V0_res.rds"), {
#
#     # Create a list to store results
#     h3_V0_res <- list()
#
#     # Get "noVacc" scenario parameters
#     h3_S0_par <- get_model3_vacc_scenario_params(scenario = "noVacc")
#     coef(h3Spat) <- p3
#     coef(h3Spat)[names(h3_S0_par)] <- h3_S0_par
#
#     # Using parameters and filtered distribution, project system
#     h3_V0_sims <- project_from_filter(
#       h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
#       nsims = NSIM, seed = 6897154
#     )
#
#     # Store nationally aggregated results
#     h3_V0_res$mod3_V0_sims <- agg_mod3_sims(h3_V0_sims)
#     h3_V0_res$mod3_V0_probs <- get_elimProbs(h3_V0_sims, model = 3)
#
#     # For the supplement material, save quantiles of the Susceptible individuals
#     h3_V0_res$SQuants <- h3_V0_sims %>%
#       mutate(
#         date = as.Date(lubridate::round_date(lubridate::date_decimal(time), unit = 'day'))
#       ) %>%
#       group_by(unitname, date) %>%
#       mutate(
#         pop = h3Spat@params[paste0("H", which(first(unitname) == unit_names(h3Spat)))]
#       ) %>%
#       summarize(
#         Q025 = quantile((S + VSd + VSdd + VSdd_alt + VSd_alt) / pop, probs = 0.025),
#         Q50 = quantile((S + VSd + VSdd + VSdd_alt + VSd_alt) / pop, probs = 0.5),
#         Q975 = quantile((S + VSd + VSdd + VSdd_alt + VSd_alt) / pop, probs = 0.975)
#       ) %>%
#       ungroup() %>%
#       rename(dep = unitname)
#
#     # Return results
#     h3_V0_res
#
#   }
# )

mod3_V1_res <- readRDS("model3/run_level_3/mod3_V1_res.rds")
# mod3_V1_res <- bake(
#   file = paste0("model3/", rl_dir, "mod3_V1_res.rds"), {
#
#     # Create a list to store results
#     h3_V1_res <- list()
#
#     # Get "noVacc" scenario parameters
#     h3_V1_par <- get_model3_vacc_scenario_params(scenario = "2dep")
#     coef(h3Spat) <- p3
#     coef(h3Spat)[names(h3_V1_par)] <- h3_V1_par
#
#     # Using parameters and filtered distribution, project system
#     h3_V1_sims <- project_from_filter(
#       h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
#       nsims = NSIM, seed = 6897154
#     )
#
#     # Store nationally aggregated results
#     h3_V1_res$mod3_V1_sims <- agg_mod3_sims(h3_V1_sims)
#     h3_V1_res$mod3_V1_probs <- get_elimProbs(h3_V1_sims, model = 3)
#
#     # Return results
#     h3_V1_res
#
#   }
# )

mod3_V2_res <- readRDS("model3/run_level_3/mod3_V2_res.rds")
# mod3_V2_res <- bake(
#   file = paste0("model3/", rl_dir, "mod3_V2_res.rds"), {
#
#     # Create a list to store results
#     h3_V2_res <- list()
#
#     # Get "noVacc" scenario parameters
#     h3_V2_par <- get_model3_vacc_scenario_params(scenario = "3dep")
#     coef(h3Spat) <- p3
#     coef(h3Spat)[names(h3_V2_par)] <- h3_V2_par
#
#     # Using parameters and filtered distribution, project system
#     h3_V2_sims <- project_from_filter(
#       h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
#       nsims = NSIM, seed = 6897154
#     )
#
#     # Store nationally aggregated results
#     h3_V2_res$mod3_V2_sims <- agg_mod3_sims(h3_V2_sims)
#     h3_V2_res$mod3_V2_probs <- get_elimProbs(h3_V2_sims, model = 3)
#
#     # Return results
#     h3_V2_res
#   }
# )

mod3_V3_res <- readRDS("model3/run_level_3/mod3_V3_res.rds")
# mod3_V3_res <- bake(
#   file = paste0("model3/", rl_dir, "mod3_V3_res.rds"), {
#
#     # Create a list to store results
#     h3_V3_res <- list()
#
#     # Get "noVacc" scenario parameters
#     h3_V3_par <- get_model3_vacc_scenario_params(scenario = "slowNation")
#     coef(h3Spat) <- p3
#     coef(h3Spat)[names(h3_V3_par)] <- h3_V3_par
#
#     # Using parameters and filtered distribution, project system
#     h3_V3_sims <- project_from_filter(
#       h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
#       nsims = NSIM, seed = 6897154
#     )
#
#     # Store nationally aggregated results
#     h3_V3_res$mod3_V3_sims <- agg_mod3_sims(h3_V3_sims)
#     h3_V3_res$mod3_V3_probs <- get_elimProbs(h3_V3_sims, model = 3)
#
#     # Return results
#     h3_V3_res
#
#   }
# )

mod3_V4_res <- readRDS("model3/run_level_3/mod3_V4_res.rds")
# mod3_V4_res <- bake(
#   file = paste0("model3/", rl_dir, "mod3_V4_res.rds"), {
#
#     # Create a list to store results
#     h3_V4_res <- list()
#
#     # Get "noVacc" scenario parameters
#     h3_V4_par <- get_model3_vacc_scenario_params(scenario = "fastNation")
#     coef(h3Spat) <- p3
#     coef(h3Spat)[names(h3_V4_par)] <- h3_V4_par
#
#     # Using parameters and filtered distribution, project system
#     h3_V4_sims <- project_from_filter(
#       h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
#       nsims = NSIM, seed = 6897154
#     )
#
#     # Store nationally aggregated results
#     h3_V4_res$mod3_V4_sims <- agg_mod3_sims(h3_V4_sims)
#     h3_V4_res$mod3_V4_probs <- get_elimProbs(h3_V4_sims, model = 3)
#
#     # Return results
#     h3_V4_res
#
#   }
# )
@

>>>>

<<Calculate Lee1 Likelihoods, echo=FALSE, message=FALSE, include=FALSE>>=

@@

<<Load Model1 Params, echo=FALSE, message=FALSE, include=FALSE>>=

@@

<<Fit Model 2, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE>>=

@@

@@

    model2_fit_results <- list()
    model2_fit_results[['h2_params']] <- h2_params
    model2_fit_results[["n_fit_params"]] <- n_fit_params
    model2_fit_results[['logLik']] <- -h2_fit_tmp$value

@@

<<Load Model3 Parameters, echo=FALSE, include=FALSE, message=FALSE>>=

# Calculate the number of parameters that are estimated:
mod3_n_params <- length(c(
  "mu_B", "XthetaA", "thetaI", "lambdaR", "r", "std_W", "epsilon", "k",
  paste0('betaB', 1:10), paste0('foi_add', 1:10),
  'aHur3', 'aHur9',
  'hHur3', 'aHur9',
  'Iinit3', 'Iinit4'
))

# Load the file containing profiles of Model 1 Parameters.
if (RUN_LEVEL != 3 && file.exists("model3/run_level_3/h3_profiles.rds")) {

  # If RUN_LEVEL != 3, and RUN_LEVEL == 3 results exist, just load the RL3
  # results.
  h3_prof <- readRDS("model3/run_level_3/h3_profiles.rds")
} else if (file.exists(paste0('model3', rl_dir, 'h3_profiles.rds'))) {

  # If the `model3/run_level_<RUN_LEVEL>/h3_profiles.rds` file exists, load it
  h3_prof <- readRDS(paste0('model3', rl_dir, 'h3_profiles.rds'))
} else {

  # Otherwise (missing RL3 file, and the corresponding <RUN_LEVEL> file):
  # Throw an error, letting users know how to create the file.
  stop(paste0("Missing file: `model3/", rl_dir, 'h3_profiles.rds`;\nThe file can be obtained by running the script `H3profile.R`'))
}

# haiti3_fit contains ll estimate for many parameter sets, so we want to find
# the highest value
mod3_ll <- h3_prof %>%
  slice_max(order_by = logLik, n = 1) %>%
  pull(logLik)
@

<<Create Model Objects,echo=FALSE,eval=TRUE, include=FALSE, message=FALSE>>=

# Save the parameters that correspond to the MLE of Model 3.
p3 <- h3_prof %>%
  slice_max(logLik, n = 1) %>%
  select(-(job.id:logLik_se)) %>%
  unlist()

unit_specific_names <- c("betaB", "foi_add", "aHur", "hHur", "Iinit")
shared_param_names <- c(
  "mu_B", "XthetaA", "thetaI", "lambdaR", "r", "std_W",
  "epsilon", "k"
)

@@

<<Get AIC table Input, echo=FALSE, eval=TRUE>>=
NREPS_EVAL <- switch(RUN_LEVEL,   3,   8,    36)
NP_EVAL    <- switch(RUN_LEVEL,  50, 500,  5000)

@@

# Calculate likelihood via block-particle filter
mod3_eval_res <- bake(
  file = paste0('model3/', rl_dir, 'mod3_eval_res.rds'), {

    # Create a list to store results
    results <- list()

    coef(h3Spat) <- p3

    # Perform block-particle filter
    h3_bpf <- foreach(i = 1:NREPS_EVAL, .combine = c) %dopar% {
      bpfilter(h3Spat, Np = NP_EVAL, block_size = 1)
    }

    ll <- logLik(h3_bpf)
    results$ll <- logmeanexp(ll[!is.na(ll)], se = FALSE)

    ### Get likelihood for subset of the data

    # Find appropriate sub-set
    in_subset_cols <- h3_bpf[[1]]@times >= as.numeric(lubridate::decimal_date(as.Date("2014-03-01")))
    in_subset_rows <- h3_bpf[[1]]@unit_names != 'Ouest'

    mod3_coupled_subset_evals <- c()
    for (i in 1:length(h3_bpf)) {
      mod3_coupled_subset_evals <- c(
        mod3_coupled_subset_evals,
        sum(h3_bpf[[i]]@block.cond.loglik[in_subset_rows, in_subset_cols])
      )
    }

    results$subset_ll <- logmeanexp(mod3_coupled_subset_evals)
    results
  },
  timing = FALSE
)

@@

<<Calculate Bench Likelihood, echo=FALSE, message=FALSE, include=FALSE, cache=TRUE>>=

@@

benchmarks[['m3']] <- m3_benchmark
rm(cases, m3_benchmark, dep, mod3_cases)
gc()
@

<<Computing AIC of Lee et al, echo=FALSE, include=FALSE, message=FALSE>>=
lee3_NP   <- switch(RUN_LEVEL, 50, 250, 5000)
lee3_NREP <- switch(RUN_LEVEL,  3,   8,   36)

@@

# Create Lee et al (2020a) version of model 3 on sub-data
lee3_sub <- lee3_spatPomp()
lee3_all <- lee3_spatPomp(start_date = "2010-10-23")

lee3_results <- bake(
  file = paste0('model3/', rl_dir, 'lee3_results.rds'), {

    # Create lists to save results
    lee3_results <- list()

    # Save how long it takes for sub-data
    lee3_results[["sub_bpf_time"]] <- system.time({

      lee3_sub_ll_evals <- foreach(
        i = 1:lee3_NREP, .combine = rbind
      ) %dopar% {

        liks <- numeric(10L)

        lee_bpf_out <- bpfilter(lee3_sub, block_size = 1, Np = lee3_NP)
        Ouest_ind <- which(lee_bpf_out@unit_names == "Ouest")

        for (u in 1:10) {
          if (u == Ouest_ind) {
            liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, lee3_sub@times >= lubridate::decimal_date(as.Date('2017-06-10'))])
          } else {
            liks[u] <- sum(lee_bpf_out@block.cond.loglik[u, ])
          }
        }

        liks
      }
    })

    # Save all likelihood evaluations
    lee3_results[["sub_ll_eval"]] <- logmeanexp(rowSums(lee3_sub_ll_evals)[!is.na(rowSums(lee3_sub_ll_evals))])

    registerDoRNG(2789131)

    # Save how long it takes for all data
    lee3_results[["all_pf_time"]] <- system.time({
      # Save all likelihood evaluations

      lee3_all_ll_evals <- foreach(
        i = 1:lee3_NREP, .combine = c
      ) %dopar% {
        logLik(bpfilter(lee3_all, block_size = 1, Np = lee3_NP))  # Get likelihood evaluations
      }

      lee3_results[["all_ll_eval"]] <- logmeanexp(lee3_all_ll_evals[!is.na(lee3_all_ll_evals)])

    })

    lee3_results[["n_params"]] <- 29

    lee3_results
  },
  timing = FALSE
)

@@

mod3_lee_coupled_aic <- 2 * lee3_results$n_params - 2 * lee3_results$all_ll_eval
mod3_lee_coupled_partial_aic <- 2 * lee3_results$n_params - 2 * lee3_results$sub_ll_eval
@

@@

<<clean Up of Betat data, echo=FALSE, message=FALSE, include=FALSE, warning=FALSE>>=
suppressWarnings(
  rm(h1_prof_res, mcap_results)
)
gc()
@

@@

# Get quantiles of simulations from the calibrated Model 3.
h3_quants <- bake(
  file = paste0('model3/', rl_dir, 'h3Sims.rds'), {

    coef(h3Spat) <- p3
    # Simulate from the fitted version of Model 3
    h3_sims <- simulate(
      h3Spat, nsim = h3_nsim, format = 'data.frame'
    )

    # For each department and time-point, calculate percentiles of the
    # simulations
    h3_sims %>%
      rename(dep = unitname) %>%
      group_by(dep, time) %>%
      summarise(
        q05 = quantile(cases, 0.025, na.rm = T),
        mean = mean(cases, na.rm = T),
        q50 = quantile(cases, 0.5, na.rm = T),
        q95 = quantile(cases, 0.975, na.rm = T)
      ) %>%
      ungroup() %>%
      mutate(
        date = lubridate::date_decimal(time)
      ) %>%
      mutate(date = as.Date(lubridate::round_date(date, unit = 'day')))
  },
  timing = FALSE
)
@

@@

<<Simulate Model 3 Vacc Scenarios, message=FALSE, include=FALSE>>=
NP_BPF <- switch(RUN_LEVEL, 20, 200, 2000)
NSIM   <- switch(RUN_LEVEL, 5,  50, 1000)

h3_bpf_end_states <- bake(
  file = paste0("model3/", rl_dir, "h3_bpf_end_states.rds"),
  expr = {
    coef(h3Spat) <- p3
    h3_bpf <- bpfilter(h3Spat, Np = NP_BPF, block_size = 1, save_states = TRUE)
    ss <- h3_bpf@saved.states
    ss[[length(ss)]]
  },
  timing = FALSE
)

mod3_V0_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V0_res.rds"), {

    # Create a list to store results
    h3_V0_res <- list()

    # Get "noVacc" scenario parameters
    h3_S0_par <- get_model3_vacc_scenario_params(scenario = "noVacc")
    coef(h3Spat) <- p3
    coef(h3Spat)[names(h3_S0_par)] <- h3_S0_par

    # Using parameters and filtered distribution, project system
    h3_V0_sims <- project_from_filter(
      h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V0_res$mod3_V0_sims <- agg_mod3_sims(h3_V0_sims)
    h3_V0_res$mod3_V0_probs <- get_elimProbs(h3_V0_sims, model = 3)

    # For the supplement material, save quantiles of the Susceptible individuals
    h3_V0_res$SQuants <- h3_V0_sims %>%
      mutate(
        date = as.Date(lubridate::round_date(lubridate::date_decimal(time), unit = 'day'))
      ) %>%
      group_by(unitname, date) %>%
      mutate(
        pop = h3Spat@params[paste0("H", which(first(unitname) == unit_names(h3Spat)))]
      ) %>%
      summarize(
        Q025 = quantile((S + VSd + VSdd + VSdd_alt + VSd_alt) / pop, probs = 0.025),
        Q50 = quantile((S + VSd + VSdd + VSdd_alt + VSd_alt) / pop, probs = 0.5),
        Q975 = quantile((S + VSd + VSdd + VSdd_alt + VSd_alt) / pop, probs = 0.975)
      ) %>%
      ungroup() %>%
      rename(dep = unitname)

    # Return results
    h3_V0_res
  }
)

mod3_V1_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V1_res.rds"), {

    # Create a list to store results
    h3_V1_res <- list()

    # Get "noVacc" scenario parameters
    h3_V1_par <- get_model3_vacc_scenario_params(scenario = "2dep")
    coef(h3Spat) <- p3
    coef(h3Spat)[names(h3_V1_par)] <- h3_V1_par

    # Using parameters and filtered distribution, project system
    h3_V1_sims <- project_from_filter(
      h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V1_res$mod3_V1_sims <- agg_mod3_sims(h3_V1_sims)
    h3_V1_res$mod3_V1_probs <- get_elimProbs(h3_V1_sims, model = 3)

    # Return results
    h3_V1_res
  }
)

mod3_V2_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V2_res.rds"), {

    # Create a list to store results
    h3_V2_res <- list()

    # Get "noVacc" scenario parameters
    h3_V2_par <- get_model3_vacc_scenario_params(scenario = "3dep")
    coef(h3Spat) <- p3
    coef(h3Spat)[names(h3_V2_par)] <- h3_V2_par

    # Using parameters and filtered distribution, project system
    h3_V2_sims <- project_from_filter(
      h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V2_res$mod3_V2_sims <- agg_mod3_sims(h3_V2_sims)
    h3_V2_res$mod3_V2_probs <- get_elimProbs(h3_V2_sims, model = 3)

    # Return results
    h3_V2_res
  }
)

mod3_V3_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V3_res.rds"), {

    # Create a list to store results
    h3_V3_res <- list()

    # Get "noVacc" scenario parameters
    h3_V3_par <- get_model3_vacc_scenario_params(scenario = "slowNation")
    coef(h3Spat) <- p3
    coef(h3Spat)[names(h3_V3_par)] <- h3_V3_par

    # Using parameters and filtered distribution, project system
    h3_V3_sims <- project_from_filter(
      h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V3_res$mod3_V3_sims <- agg_mod3_sims(h3_V3_sims)
    h3_V3_res$mod3_V3_probs <- get_elimProbs(h3_V3_sims, model = 3)

    # Return results
    h3_V3_res
  }
)

mod3_V4_res <- bake(
  file = paste0("model3/", rl_dir, "mod3_V4_res.rds"), {

    # Create a list to store results
    h3_V4_res <- list()

    # Get "noVacc" scenario parameters
    h3_V4_par <- get_model3_vacc_scenario_params(scenario = "fastNation")
    coef(h3Spat) <- p3
    coef(h3Spat)[names(h3_V4_par)] <- h3_V4_par

    # Using parameters and filtered distribution, project system
    h3_V4_sims <- project_from_filter(
      h3Spat, end_states = h3_bpf_end_states, covarGen = project_rain,
      nsims = NSIM, seed = 6897154
    )

    # Store nationally aggregated results
    h3_V4_res$mod3_V4_sims <- agg_mod3_sims(h3_V4_sims)
    h3_V4_res$mod3_V4_probs <- get_elimProbs(h3_V4_sims, model = 3)

    # Return results
    h3_V4_res
  }
)
@
